### 2019-06-30 papers/journal/intro.tex
intro rewritten

%\subsection{Synthesis of VTS:}
%
The set of basic constraints the VTS should follow is dictated by underlying cell biology.   
%
In order to attempt to complete a given partial VTS, we have to first agree on the properties that every complete VTS should follow in spite of the basic constraints. 
%
We can use our graph connectivity results as a basis for this investigation.   
%
The incomplete VTS might not respect these constraints. 
%
In this paper, using constraints on global vesicle traffic network topology due to local molecular interactions, we take incomplete pictures of vesicle traffic networks as inputs.
%
We output various completed versions of VTS against these properties which can then be tested experimentally.
%

\subsection{Analysis is difficult problem}
The analysis of VTSs is a difficult problem because
of the combinatorial scaling of possible traffic topologies and
regulatory rules.
%
If the analysis is done on a large number of graphs, the joined effect of this with combinatorially many possible regulatory rules will be difficult to handle by any tool.
%
Precise analysis of the properties of the VTS would be hindered for the same reason.

@@

%These tools are central to formal verification methods in computer science, and are increasingly being applied to understand biological systems, including gene regulatory networks [16-18]. 
\subsection{Previous work and our Contribution}

As CBMC does not directly support solving such
quantified formulas, we had to use a technique that combined
non-determinism and partial enumeration that is not as
efficient.\newline

%
In this paper, we have developed a novel SAT encoding for
searching a VTS that satisfy the given properties.
%
We improved the encoding of some of the conditions for VTSs.
%
In the earlier implementation, reachability was encoded by
enumeration of paths.
%
In our encoding, we have recursively defined the reachability condition
such that that we avoid the exponential enumeration.
%
We have also encoded $k$-connectivity in the similar fashion and
avoided a blowup in the formula size.
%

We have implemented the encoding using Z3~\cite{z3} python API and searched for
VTS satisfying various properties upto size 14-18 nodes as compare
earlier tool that could only search graph upto size 7-8 nodes.
%
Since most VTSs in the cells are of 10 compartments,
our tool will be useful for biologists to study VTSs.
%
Furthermore, our encoding supports several variations of
the conditions.\newline

The following are the contributions of this work:
\begin{itemize}
	\item We have added novel encoding reachability and 3-4 connectivity
	\item Direct encoding into the SAT solver
	\item A user friendly and scalable tool based on well known SMT solver Z3
\end{itemize}

\par We have implemented the encoding in a flexible tool, which can handle a wide range of synthesis queries. 
%
We have applied our tool on several VTSs including
two found-in-nature VTSs.
%
Our experiments suggest that some of the synthesis problems are solvable by modern solvers and the synthesis technology may be useful for biological research.
%

>>>>

%\subsection{Synthesis of VTS:}
%
The set of basic constraints the VTS should follow is dictated by underlying cell biology.   
%
In order to attempt to complete a given partial VTS, we have to first agree on the properties that every complete VTS should follow in spite of the basic constraints. 
%
We use our graph connectivity results as a basis for this investigation.   
%
The incomplete VTS might not respect these constraints. 
%
In this paper, using constraints on global vesicle traffic network topology due to local molecular interactions, we take incomplete pictures of vesicle traffic networks as inputs.
%
We output various completed versions of VTS against these properties which can then be tested experimentally.
%

%\subsection{Analysis is difficult problem}
The analysis of VTSs is a difficult problem because
of the combinatorial scaling of possible traffic topologies and
regulatory rules.
%
Analysis on a large number of graphs~\footnote{There are total 68715 simple (no parallel edges) 3-connected graphs with 8 nodes} jointly with combinatorially many possible regulatory rules (all compatible labels of edges and nodes etc.) will be difficult to handle by any tool.
%
Precise analysis of the properties of the VTS would be hindered for the same reason.

@@

In a recent work \cite{shukla2017discovering}, we employed the model checker CBMC \cite{ckl2004} meant to analyze ANSI C programs for studying this problem. 
%
VTSs and SNARE regulations were modeled as C code using arrays to represent graphs and Boolean tables. 
%
The graph connectivity question for different variations of SNARE regulations were modeled as logical assertions to be checked by the model checker. 
%
Although the performance was satisfactory the encoding was non-optimal and hence scalability of the method was insufficient (the tool was able to handle system with just 8 compartments).
%
Another interesting question of property involving quantifiers (was termed as sufficient condition in \cite{shukla2017discovering}; in this paper we call it universal condition) was partly handled using sampling and left open as a future work.
%
In this paper we present both the SMT and QBF encoding to address these two problems.
%
%These tools are central to formal verification methods in computer science, and are increasingly being applied to understand biological systems, including gene regulatory networks [16-18]. 
%\subsection{Previous work and our Contribution}
%
%The following are the contributions of this work:
%\begin{itemize}
%	\item We have added novel encoding reachability and 3-4 connectivity
%	\item Direct encoding into the SAT solver
%	\item A user friendly and scalable tool based on well known SMT solver Z3
%\end{itemize}

\par We have implemented the encoding in a flexible tool, which can handle both connectivity question and a wide range of synthesis queries. 
%
%
We have applied our synthesis tool on several VTSs including
two found-in-nature VTSs.
%
We manage to scale the tool upto the size that makes tool biologically relevant. 
%
Our experiments suggest that some of the synthesis problems are solvable by modern solvers and the synthesis technology may be useful for biological research.
%
